Practical implications of HATEOAS on a bridge between LOD and SPARQL

### 2012-02-29 eswc-2012/workshop.tex
strong->emph
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@130 43ef1190-90fd-4dd7-a769-d0121f02b80e

In most cases, the current information resource will be the subject of
the \texttt{hm:operations} \strong{but also} the object of the allowed
operations. A typical information resource will supply the following
triples (given a suitable base URI):

>>>>

In most cases, the current information resource will be the subject of
the \texttt{hm:operations} \emph{but also} the object of the allowed
operations. A typical information resource will supply the following
triples (given a suitable base URI):
